Interactive Visual Analysis of Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-12-10 draft.tex
updated supplementary material URL

%The analysis, as well as the presented IVA tool is available as supplementary material in an interactive \texttt{R Markdown}\footnote{Developed by RStudio, Inc; \texttt{rmarkdown.rstudio.com}} document (\url{blind.dnsalias.com}).

@@

% The complete analysis can be found in the experiments section of the supplementary material (\url{blind.dnsalias.com})

@@

The resulting contingency matrices show no strong correlation with image variables (see experiments page at \url{blind.dnsalias.com}).

@@

All analyses are available at \url{blind.dnsalias.com} and are carried out using \texttt{R}, a widely used programming language for statistical calculations and visualizations.

@@

% The prototype is available at \url{blind.dnsalias.com}.

@@

%\section*{\uppercase{Appendix}}
%\noindent The IVA tool and all shown plots presented in this paper are available as supplementary material under the following link: \url{blind.dnsalias.com}.

>>>>

%The analysis, as well as the presented IVA tool is available as supplementary material in an interactive \texttt{R Markdown}\footnote{Developed by RStudio, Inc; \texttt{rmarkdown.rstudio.com}} document (\url{ivapp15.dnsalias.com}).

@@

% The complete analysis can be found in the experiments section of the supplementary material (\url{ivapp15.dnsalias.com})

@@

The resulting contingency matrices show no strong correlation with image variables (see experiments page at \url{ivapp15.dnsalias.com}).

@@

All analyses are available at \url{ivapp15.dnsalias.com} and are carried out using \texttt{R}, a widely used programming language for statistical calculations and visualizations.

@@

% The prototype is available at \url{ivapp15.dnsalias.com}.

@@

%\section*{\uppercase{Appendix}}
%\noindent The IVA tool and all shown plots presented in this paper are available as supplementary material under the following link: \url{ivapp15.dnsalias.com}.
